On Determinism of Game Engines used for Simulation-based Autonomous Vehicle Verification

### 2022-02-02 document/ieee_trans/det_ieeetrans.tex
update bios

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{../other/mugs/greg.png}}]{Greg Chance}
received the B.Sc. (Hons.) and Ph.D. degrees in physics from the University of Bath, Bath, U.K., in 2001 and 2005, respectively. He was previously at the Bristol Robotics Lab and is currently a Senior Research Associate with the Trustworthy Systems Laboratory, University of Bristol, Bristol, U.K. His current research interests are simulation-based verification for autonomous systems and cybersecurity. He has ten years industrial experience researching for Oxford Instruments, U.K., and BAE Systems, U.K. Dr Chance is a Chartered Engineer and a member of the Institute of Physics and holds a patent for a novel plasma control method. 
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{../other/mugs/abanoub}}]{Abanoub Ghobrial}
received the MEng degree in mechanical engineering from the University of Bristol, Bristol,  U.K., in 2018. He is currently pursuing the Ph.D. degree in computer science at the University of Bristol and is a part-time Research Associate with the Trustworthy Systems Lab, Bristol,  U.K. From 2018 to 2020, he was a full-time Research Associate with the Trustworthy Systems Lab. His current research interests are techniques to allow self-managing of autonomous safety-critical systems via continual learning during operation; and the development of simulation-based verification techniques for autonomous systems.
\end{IEEEbiography}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{../other/mugs/greg.png}}]{Greg Chance}
received the B.Sc. (Hons.) and Ph.D.\ degrees in physics from the University of Bath, in 2001 and 2005, respectively. He was previously at the Bristol Robotics Lab and is currently a Senior Research Associate with the Trustworthy Systems Laboratory, University of Bristol. His current research interests are simulation-based verification for autonomous systems and cybersecurity. He has ten years industrial experience researching for Oxford Instruments, and BAE Systems. Dr Chance is a Chartered Engineer and a member of the Institute of Physics and holds a patent for a novel plasma control method. 
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{../other/mugs/abanoub}}]{Abanoub Ghobrial}
received an MEng degree in mechanical engineering from the University of Bristol in 2018. He is currently pursuing a Ph.D.\ degree in computer science at the University of Bristol and is a part-time Research Associate with the Trustworthy Systems Lab, where he was a full-time Research Associate from 2018 to 2020. His current research interests are techniques to allow self-managing of autonomous safety-critical systems via continual learning during operation and the development of simulation-based verification techniques for autonomous systems.
\end{IEEEbiography}
